Cosmic evolution of the correlation between supermassive black hole mass and host galaxy at redshift up to 1.7

### 2019-01-14 manuscript/manuscript.tex
update for the paper draft

\shorttitle{ShortTitle}
\shortauthors{X. Ding et al.}

@@

\title{QSO decomposition}

\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{1}, John Silverman\altaffilmark{3}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Simon Birrer\altaffilmark{1}, Malte Schramm\altaffilmark{6}, Andreas Schulze\altaffilmark{6}
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, Università Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}
To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written.  To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

@@

Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN. The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

Despite the great amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works. First, the inherent uncertainties in BH mass estimates using the virial method. Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties. It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Equally important,
the selection effects and their impact on the observed need to be taken well into account. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.

To make progress, it is essential to make use of the larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh. On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.

In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass to redshift at $z>1$. For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$. The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, a near-infrared (0.9-1.8 $\mu m$) spectrograph have with 400 apertures. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.

Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{blue}{\bf (32+4?, the information of these four sample?)}. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.

To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.

\subsection{Observation and reduction}
\label{observation}
\subsubsection{HST image Observation}
% The QSO surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the stellar of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection could ensure that the broad \halpha\ line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 with a \texttt{gaussian} kernel. \textcolor{blue}{The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).}
To accurately estimate the background light which could come from both the sky and the detector, we also adopt the {\sc photutils} to measure the photometry.

%With 27/36 of our AGNs having rest-frame UV imaging with HST (COSMOS: F814W, PI: Nicholas Scoville; GEMS: F606W+F850LP), we are able to infer the host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009}.

21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. %arxiv: 0702359}.
Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the motion of the BLR gas is virialised by the gravity. In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to this paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt the list of consistent ones to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the QSO imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations. The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}. Empirical PSF stars are considered better than the simulated ones, since they we observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by cutting out the isolated, unsaturated PSF stars with high S/N from the overall QSO field. We first collect the identified stars as candidates which are listed in the COSMOS2015 catalog by \citet{Laigle2016}. However, since a lot of bright stars with intensity similar to the QSOs are excluded by \citet{Laigle2016}, we visually select these star-like PSF as candidates. Finally, we remove the non-ideal PSF candidates by inspecting their intensity, FWHM, central symmetry and any that were contaminated by background objects. To summarize, we selected 78 and 36 PSFs from the field observed by filter F140W and F125W, respectively.

We stress that, by building this library, we assume that the PSFs herein bracket all the possible PSF light distribution which fits our imaging data. Therefore, the inference from each PSF will include the true answer. In the next subsection, we carry out the QSO decomposition using each PSF. We rank their performance based on the goodness (i.e. $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy. Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be even more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample. Furthermore, we fit the galaxies which close to the QSO as the \sersic\ model, to account for the contamination of their light.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy}, to decompose the host and nuclear light. The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package. 
The flexibility of this package enable us to turn off the lensing channel and carry out this task\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modelling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}. The input ingredients to \lenstronomy\ includes:
\begin{enumerate}
\item \hst\ AGN imaging data. -- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ cover sufficient QSO light our samples. By default, we cut out the AGN image to a $61\times61$ pixels box (i.e. $4''\times 4''$). 
\item Noise level map -- The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. 
\item PSF -- The PSF are directly taken from the PSF library. Usually, mismatch exists when subtract the AGN as the scaled PSF, especially at the central parts. We assume that the overall inference based on each PSF bracket the best one as one can obtain, given the flexibility of the library. We also note that, in the lens modelling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.  However, this approach collects the information of the lensing feature which is not suitable to our case. If one forces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
\end{enumerate}

%Introduce the final inference using fitting:
Focusing on each QSO system, its host light information is inferred through several steps. First, we fit the flux distribution using each PSFs in the library. Given the fitting ingredients, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals. In this step, we apply the Particle Swarm Optimizer (PSO) to optimize the best-fit parameters based on the imaging likelihood. Running through the library, we record the inference based on each PSF together with the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval. However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}. In the second step, we rank the performance of each PSF based on the $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property. The weights for each PSF is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is the inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
\end{eqnarray} 
Note that since each QSO system has different seeing condition, the top-8 PSFs are different for each system.

%ECDFS-358 and CID206
In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized results inferred by \lenstronomy. In each, we show the images, best-fit models, image subtract point source (i.e. host) and the residuals for every systems. As an example, we also show the weighting process for system CID1174 in Table~\ref{tab:weight_CID1174}. To quickly overview our inference, we summarize them as relations between: 1) effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

%The inference of F814w data.
18/32 systems in COSMOS field have ACS/F184W imaging data. Likewise, we infer their host properties using the same approach. The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library. While fitting the host light, we fix the \Reff\ and \sersic\ $n$ as the value inferred by WFC3/IR, assuming that the shape of the galaxy are consistent between ACS and WFC3. We believe the inferred information of the galaxy shape by IR imaging are superior to the one by UV band, considering the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band.

@@

\section{Summary}
\label{sec:sum}
We presented the study of the Mbh and host property's evolution to high redshift until 1.8.

>>>>

\shorttitle{Cosmic evolution of the \mbh-host relation}
\shortauthors{X. Ding et al.}

@@

\title{Cosmic evolution of the correlation between supermassive black hole mass and host galaxy at redshift up to 1.7}

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2}, Knud Jahnke, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, Università Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}
We investigate the cosmic evolution of the relation supermassive black hole and host galaxy properties at $1.2<z<1.7$, using a sample of 32 X-ray selected type-1 AGN obtained with the Hubble Space Telescope (\hst). The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosities (\lhost) and stellar masses (\smass). We estimate the BH masses (\mbh) with spectroscopic information of the \halpha, \hbeta. We compare the \mbh-\lhost and \mbh-\smass relation to the local active galaxies and taking the selection effects into account.
Results to be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

@@

Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

One key to this study is tracing their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on our understanding at $z<1$ using the type 1 AGN. The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ is elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

Despite the enormous amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works. First, the inherent uncertainties in BH mass estimates using the virial method. Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties. It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extending the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Equally important, the selection effects and their impact on the observed need to be taken well into account. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.

To make progress, it is essential to make use of the larger sample to high-quality data in respect of the measurement of both the host properties and the \mbh. On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improve the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.

In this study, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$. For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$. The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, a near-infrared (0.9-1.8 $\mu m$) spectrograph have with 400 apertures. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}. Overall, our final sample is composed of 32 new observations by HST/WFC3. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. 
To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.

\subsection{Observation and reduction}
\label{observation}
\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection could ensure that the broad \halpha\ line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel. 
To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.

Multi-band information provides the spectral energy distributions (SED) at a more precise level. 21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity virializes the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to this paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations. The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}. Empirical PSF stars are considered better than the simulated ones, since they were observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by selecting the isolated, unsaturated PSF-stars with high S/N from the overall AGN field. The selection is completed by the following steps. We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}. A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates. We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects. Finally, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.

We assume that the overall PSF-stars in the library cover all possible PSF light distribution. Therefore, when fitting to data, the entire inference would bracket the true answer.
%In the next subsection, we carry out the AGN decomposition using each PSF. We rank their performance based on the goodness (i.e. $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy. As a common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be even more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample. Furthermore, we fit the galaxies which close to the AGN as the \sersic\ model, to account for the contamination of their light.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy} to perform the decomposition of the host and nuclear light. \lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package. 
Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}. The input ingredients to \lenstronomy\ include:
\begin{enumerate}
\item AGN imaging data. \\
-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ covers sufficient AGN light our samples. By default, we cut out the AGN image to a $61\times61$ pixels box (i.e. $4''\times 4''$). If needed, the larger size box would be sufficient to include the nearby objects. 
\item Noise level map.\\
-- The origin of the noise in each pixel stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. 
\item PSF. \\
-- 
The PSF is directly taken from the PSF library. Usually, the mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts. We also note that, in the lens modeling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.  However, this approach incorporates with the information of the lensing feature which is not suitable for our case. If one enforces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference. Hopefully, our library contains sufficient information to cover all the possible PSF, and the entire inference would bracket the true answer. 
\end{enumerate}

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred through several steps. First, we decompose the AGN-host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
To avoid any unphysical inference, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$. Since the inference by each PSF could be the right answer, we save all of them as our entire inference. Then, we extract the best answer from the entire inference. We rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs. We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using weighted arithmetic mean, and the weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is the inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
\end{eqnarray} 
Note that since each AGN system has different seeing condition, the top-eight PSFs are usually varies from one AGN system to another. Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{8}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{8}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

%ECDFS-358 and CID206
In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals. As an example, the weighting values in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

The inference of the host properties is weighted by eight top-ranked PSFs. To understand how the amount of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.

%The inference of F814w data.
18/32 systems in the COSMOS field have ACS/F184W imaging data. Likewise, we infer their host properties using the same approach. The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library. In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host. Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.

@@

\section{Summary}
\label{sec:sum}
%We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
